Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-09-25 doc/JFLA2022/paper.tex
and -> ampersand (atricle)
new title
fill in affiliation
small change

%% Front Matter
%%
% Regular title as in the article class.
%
\title{Hydras and Co.  \\
  Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq}

@@

\section{Main features}

>>>>

%% Front Matter
%%
% Regular title as in the article class.
%
\title{Hydras, Ordinals \&  Co.  \\
  A library in Coq of entertaining formal mathematics}

@@

 \TODO[Pierre]{Using equations for $H'$ as rewrite rules, we could prove nice minorations: for instance, the number $H'_{\omega^3}(3)$ has at least $2^{10^{21}}$ binary digits.}
\section{Main features}
